Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-04 Master Thesis/synopsis.tex
Better helper lemma

\begin{lemma}\label{lemma-spvd}
Let $K$ be a finitely generated field of dimension $2$. Then we have:
\begin{enumerate}[(i)]
\item $\operatorname{Spv}^{(2)}(K) = \operatorname{Spv}^{(2)}_\text{d}(K) = \operatorname{Spv}^{(2)}_\text{rd}(K)$
\item $\operatorname{Spv}(K) = \operatorname{Spv}_\text{d}(K)$
\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}[(i)]
\item Let $v\in\operatorname{Spv}^{(2)}(K)\subset |\operatorname{Spv}(K)|$. By Lemma \ref{2.2-prepre} we have $\dim k(v) = 0$ and thus the equality of the dimension inequality. By Lemma \ref{dimension-equality} $\Gamma_v$ is a finitely generated abelian group of rank $2$, thus not a subgroup of $\mathbb{R}$, i.e. $\operatorname{rank}(v)> 1$. 
\item Let $v\in\operatorname{Spv}(K)$. If $\operatorname{rank}(v) = 2$, the assertion follows from Lemma \ref{rank-dimension-inequality}. If $\operatorname{rank}(v) = 0$, the value group $\Gamma_v$ is trivial, thus $\operatorname{rrank}(v) = 0$ as well. If $\operatorname{rank}(v) = 1$ and $\operatorname{rrank}(v) = 2$, we have $v\in\operatorname{Spv}^{(2)}_\text{d}(K)$ by (i), a contradiction. \qedhere
\end{enumerate}
\end{proof}

>>>>

\begin{lemma}\label{lemma-spvd}
Let $K$ be a finitely generated field of dimension $2$. Then we have:
\begin{enumerate}[(i)]
\item $\operatorname{Spv}^{(2)}(K) = \operatorname{Spv}^{(2)}_\text{d}(K) = \operatorname{Spv}^{(2)}_\text{rd}(K)$
\item $\operatorname{Spv}^{(1)}(K) = \operatorname{Spv}^{(1)}_\text{d}(K)$
\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}[(i)]
\item Let $v\in\operatorname{Spv}^{(2)}(K)\subset |\operatorname{Spv}(K)|$. By Lemma \ref{2.2-prepre} we have $\dim k(v) = 0$ and thus the equality of the dimension inequality in Lemma \ref{rank-dimension-inequality}. By Lemma \ref{dimension-equality} $\Gamma_v$ is a finitely generated abelian group of rank $2$, thus not a subgroup of $\mathbb{R}$, i.e. $\operatorname{rank}(v)> 1$. 
\item Let $v\in\operatorname{Spv}^{(1)}(K)$. If $\operatorname{rank}(v) = 0$, $v$ would be the trivial valuation with trivial value group $\Gamma_v = 0$ and rational rank $0$. \qedhere
\end{enumerate}
\end{proof}
